%!TEX root = main.tex
\section{Precise Visual Querying\label{sec:precise}}
Visual analysis is valuable often reveal important -----. However, there are many -----. 

\subsection{Motivating Example}
Astronomers from the The Dark Energy Survey (DES)\cite{Drlica-Wagner2017} are interested in finding anomalous time series to discover astrophysical transients (objects whose brightness changes dramatically as a function of time), such as supernova explosions or quasars. When trying to find celestial objects corresponding to supernovae, which have a specific pattern of brightness over time, scientists need to individually inspect the visualizations of each object until they find ones that match the pattern. With more than 400 million objects in their catalog, each having their own set of time series brightness measurement, the process of manually exploring a large number of visualizations is not only error-prone, but also overwhelming for scientists who do not have extensive knowledge about their dataset.  

% Intention driven task-based querying (Precise search)
\subsection{Challenges}
\par The astronomy use case highlights a common challenge in exploratory data analysis (EDA). There is often a large space of possible visualizations that could be generated from a given dataset and manual search through this large collection is inefficient.
\par There has been many related work in this ------- varying different space of possible visualizations, including visual encodings------data facets, . We will focus on 


Data is agnostic to the user, intention ---, by building tools---, Section \ref{sec:precise} to \ref{sec:vague} have focussed on extracting what user want from data. bridging together what user want from data, what data has to offer, supporting interactive discourse between the two. 

There’s a large space of possibilities, manual search is tedious. Either using one-size-fits-all statistics, templates, heuristics as a solution or problem only applicable to a subset of analytic tasks\cite{Vartak2015,Vartak2017}. Propose VQS as a solution\cite{Lee2017}. 
\subsubsection{Usage Scenario}
\subsection{Effortless Data Exploration with \zv}
\begin{itemize}
	\item ZQL offers a way to iterate over collections of visualizations\cite{Wongsuphasawat2016}. Iterate over collections of visualizations \cite{Siddiqui}
	\item 
\end{itemize}

\subsection{Challenges Ahead}
The goal here is to help novice submit precise queries without SQL background, easy to use interface. Our study found that VQS does more than just this, but still not enough.
\begin{itemize}
	\item Precise Search Fail to understand intricacies of user need/intent, need more expressivity/flexibility for querying.
	\item  No perfect training workload, real-world data + task is noisy and complex. 
	\item towards more holistic model for insight discovery
\end{itemize}
