\documentclass[11pt]{article}
\usepackage{deauthor}
\usepackage{times}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage[square,numbers]{natbib}

\newenvironment{denselist}{
    \begin{list}{\small{$\bullet$}}%
    {\setlength{\itemsep}{0ex} \setlength{\topsep}{0ex}
    \setlength{\parsep}{0pt} \setlength{\itemindent}{0pt}
    \setlength{\leftmargin}{1.5em}
    \setlength{\partopsep}{0pt}}}%
    {\end{list}}

\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}
      \setlength{\parsep}{2pt}
      \setlength{\topsep}{0pt}
      \setlength{\partopsep}{0pt}
      \leftmargin=25pt
\rightmargin=0pt
\labelsep=5pt
\labelwidth=10pt
\itemindent=0pt
\listparindent=0pt
\itemsep=\parsep
    }
}
\newcommand{\squishend}{\end{list}}

% use extensively to toggle between paper and TR
\newcommand{\eat}[1]{}
% \newcommand{\papertext}[1]{{\leavevmode\color{blue}{#1}}}
% \newcommand{\techreport}[1]{{\leavevmode\color{red}{#1}}}
\newcommand{\papertext}[1]{#1}
\newcommand{\techreport}[1]{}
\newcommand{\boldpara}[1]{\textbf{\paragraph{#1}}}
% de-facto paragraph format
\newcommand{\stitle}[1]{\par\noindent\textbf{#1}}
\newcommand{\tvcg}[1]{{\leavevmode\color{blue}{#1}}}
\newcommand{\cut}[1]{{\leavevmode\color{lightgray}{#1}}}
\newcommand{\ccut}[1]{} %confirmed cut
\def\plainauthor{Doris Jung-Lin Lee, Aditya Parameswaran}
\def\emptyauthor{} 
\def\plainkeywords{Data visualization, exploratory data analysis, visual querying.}
\def\plaingeneralterms{Documentation, Standardization}

\newcommand{\zv}{\textit{zenvisage}\xspace}
\newcommand{\sbd}{\textsc{Storyboard}\xspace}
\newcommand{\agp}[1]{\textcolor{green}{Aditya: #1}}
\newcommand{\dor}[1]{\textcolor{blue}{Doris: #1}} 

\newcommand\notes[1]{\textcolor{red}{#1}}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Towards a Holistic Workflow for Visual Data exploration}
\author{\plainauthor\\
\{jlee782,adityagp\}@illinois.edu\\
University of Illinois, Urbana-Champaign}
\maketitle
\begin{abstract}
Visualization is one of the most effective and widely-used techniques for understanding data. Yet, the growing use of visualizations for exploratory data analysis presses new demands beyond simply the graphical presentation and visualization authoring capabilities offered in existing tools. In this paper, we describe three areas of visual data exploration facing these challenges. First, we introduce the problem of precise querying, which involves how to search for a desired pattern and operate on large collections of visualizations. As vague and complex queries cannot often be addressed through interactions in precise visual querying system, we introduce a class of intelligent visual querying systems that allows users to clarify and refine their queries. Finally, even with a omnipotent system that addresses any given visual query, users may not know what to query. Therefore, we advocate for recommendations that facillitates distributional and contextual awareness to help users gain more holistic data understanding, guide them towards meaningful insights, and jumpstart further inquiries. We describe the exemplary systems drawing from both our own work (\zv and \sbd) and ongoing research in the area to highlight future directions and opportunties in this space.

% This paper surveys the emerging field of formally reasoning
% about and optimizing open-ended crowdsourcing, a popular and crucially important, but severely
% understudied class of crowdsourcing—the next frontier in crowdsourced data management. The underlying
% challenges include distilling the right answer when none of the workers agree with each other,
% teasing apart the various perspectives adopted by workers when answering tasks, and effectively selecting
% between the many open-ended operators appropriate for a problem. We describe the approaches that
% we’ve found to be effective for open-ended crowdsourcing, drawing from our experiences in this space.
\end{abstract}

% Eventually, we need to compile all of these into one single file  during submission time. 
\input{0-Introduction}
\input{1-PreciseSearch}
\input{2-HypothesisFormation}
\input{3-IntelligentSearch}
\input{4-DatasetUnderstanding}
\input{5-Conclusion}

{\footnotesize \bibliographystyle{named}
\bibliography{reference}}
\end{document}
